Papers

### 2023-10-07 quarto/index.qmd
update

* C. Qin, **A. Zhang**, Z. Zhang, J. Chen, M. Yasunaga, and D. Yang<br>
<a href="https://arxiv.org/abs/2302.06476" target="_blank">Is ChatGPT a General-Purpose Natural Language Processing Task Solver?</a><br>
*"Can ChatGPT solve, for example, sequence tagging?"*
In *arXiv*, 2023<br>

@@

>>>>

@@

* C. Qin, **A. Zhang**, Z. Zhang, J. Chen, M. Yasunaga, and D. Yang<br>
<a href="https://arxiv.org/abs/2302.06476" target="_blank">Is ChatGPT a General-Purpose Natural Language Processing Task Solver?</a><br>
In *Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>

* J. Chen, **A. Zhang**, D. Yang, M. Li, and A. J. Smola<br>
<a href="https://arxiv.org/abs/2304.04746" target="_blank">A Cheaper and Better Diffusion Language Model with Soft-Masked Noise</a><br>
In *Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>
<a href="https://github.com/amazon-science/masked-diffusion-lm" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

### 2023-10-07 quarto/papers.qmd
update

* J. Chen, **A. Zhang**, M. Li, A. J. Smola, and D. Yang<br>
<a href="https://arxiv.org/abs/2304.04746" target="_blank">A Cheaper and Better Diffusion Language Model with Soft-Masked Noise</a><br>
*"Train diffusion language models faster with masks."*
In *arXiv*, 2023<br>
<a href="https://github.com/amazon-science/masked-diffusion-lm" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

@@

* A. Chan, Y. Tay, Y. S. Ong, and **A. Zhang**<br>
**Poison Attacks against Text Datasets with Conditional Adversarially Regularized Autoencoder**<br>
In *Findings of Empirical Methods in Natural Language Processing* (**EMNLP-Findings**), 2020

>>>>

* C. Qin, **A. Zhang**, Z. Zhang, J. Chen, M. Yasunaga, and D. Yang<br>
<a href="https://arxiv.org/abs/2302.06476" target="_blank">Is ChatGPT a General-Purpose Natural Language Processing Task Solver?</a><br>
In *Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>

* J. Chen, **A. Zhang**, D. Yang, M. Li, and A. J. Smola<br>
<a href="https://arxiv.org/abs/2304.04746" target="_blank">A Cheaper and Better Diffusion Language Model with Soft-Masked Noise</a><br>
In *Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>
<a href="https://github.com/amazon-science/masked-diffusion-lm" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* R. Aly, X. Shi, K. Lin, **A. Zhang**, and A. G. Wilson<br>
<a href="https://arxiv.org/abs/2305.12576" target="_blank">Automated Few-Shot Learning with Instruction-Finetuned Language Models</a><br>
In *Findings of Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>

@@

* A. Chan, Y. Tay, Y. S. Ong, and **A. Zhang**<br>
**Poison Attacks against Text Datasets with Conditional Adversarially Regularized Autoencoder**<br>
In *Findings of Empirical Methods in Natural Language Processing* (**EMNLP**), 2020
